\documentclass[10pt]{article}

\usepackage{amsmath}
\usepackage{amssymb}

\setlength{\textwidth}{5.7truein}
\setlength{\textheight}{9.7truein}
\setlength{\oddsidemargin}{3.0mm}
\setlength{\evensidemargin}{3.0mm}
\setlength{\topmargin}{-23.5truemm}
\setlength{\parindent}{0.0truemm}
\parskip=1mm

\title{\bf DECO3801 User Testing Document}
\author{Scott Heiner}

\date{}

\begin{document}

\maketitle

Name: $\underline{\hspace{4cm}}$

Program or Degree: $\underline{\hspace{5cm}}$ \\ \\

Please wait for your instructions from supervisors before completing these scenarios. Time will be taken between each scenario to write down key information.

\subsection*{Get Informed}

Navigate to the help page. Since this is your first time using the software, read up on what the error bars mean here.

\subsection*{Direct Input}

Copy some basic HTML text into the Direct Input page, and validate it for errors. This can be from a file you have locally, or you can use the following provided code:
\begin{verbatim}
<html>
	<head></head>
	<body></body>
</html>
\end{verbatim}

\subsection*{Upload File}

Upload a file to the Upload File page, and validate it for errors. If you do not have a file of your own, we can provide you with one.

\subsection*{Fixing a File}

Based on the error messages provided, fix your uploaded file and resubmit it.

\subsection*{Upload Zip}

Upload a zipped website to the Upload Zip page, and validate it for errors. If you do not have a website of your own, we can provide you with one.

\subsection*{Upload Non-HTML File}

Try uploading any file you like. Does the application behave well?

\newpage
\section*{Questionnaire}

\begin{enumerate}
\item Have you taken DECO1400/DECO7140? If not, do you have any past learning experience in web design (such as HTML4, Javascript, etc). \\ $\square$ Yes $\square$ No \\ Past learning experience: $\underline{\hspace{4cm}}$
\item Do you have any programming background, if so what languages you have been using? \\ $\square$ Yes $\square$ No \\ Past learning experience: $\underline{\hspace{4cm}}$
\item How likely would you use this tool to assist you in your study? \\ 
\begin{center}
\begin{tabular}{r | c | c | c | l}
Very likely & ~ & ~ & ~ & Very unlikely \\
5 & 4 & 3 & 2 & 1
\end{tabular}
\end{center}
\item How visually appealing is the website to you? \\
\begin{center}
\begin{tabular}{r | c | c | c | l}
Very appealing & ~ & ~ & ~ & Not very appealing \\
5 & 4 & 3 & 2 & 1
\end{tabular}
\end{center}
\item How well did this tool meet your expectations? \\
\begin{center}
\begin{tabular}{r | c | c | c | l}
Met my expectations very well & ~ & ~ & ~ & Did not meet my expectations \\
5 & 4 & 3 & 2 & 1
\end{tabular}
\end{center}
\item Do you feel comfortable with the presentation of the error message(s)? \\
\begin{center}
\begin{tabular}{r | c | c | c | l}
Very comfortable & ~ & ~ & ~ & Not very comfortable \\
5 & 4 & 3 & 2 & 1
\end{tabular}
\end{center}
\item How easy did you find the tool to navigate?
\begin{center}
\begin{tabular}{r | c | c | c | l}
Very easy & ~ & ~ & ~ & Very difficult \\
5 & 4 & 3 & 2 & 1
\end{tabular}
\end{center}
\item Is this your first time using HTML5 in developing a website? \\ $\square$ Yes $\square$ No
\item Would you prefer the option to select multiple files at once (in the explorer window) when uploading? \\ $\square$ Yes $\square$ No
\item If you have any general feedback/suggestions, feel free to use the space below to tell us. \\ \\
\setlength{\unitlength}{1cm}
\begin{picture}(12,5)
\put(0,0){\framebox(12,5){}}
\end{picture}
\end{enumerate}

\end{document}