\documentclass[12pt]{article}

\usepackage{amsmath}
\usepackage{amssymb}

\setlength{\textwidth}{5.7truein}
\setlength{\textheight}{9.7truein}
\setlength{\oddsidemargin}{3.0mm}
\setlength{\evensidemargin}{3.0mm}
\setlength{\topmargin}{-23.5truemm}
\setlength{\parindent}{0.0truemm}
\parskip=1mm

\title{\bf DECO3801 2 Minute Pitch}
\author{Scott Heiner on behalf of THEM}

\date{}

\begin{document}

\maketitle

\section*{Scripted Version}

The new HTML5 specification is forgiving and tolerant. Older validators for HTML 4 are no longer relevant for the new standard in web design. These two issues do no favours to those who teach best practice in web design. Usually, students miss key areas of web design like accessibility, and accidentally fall into bad practices. Our client, Lorna Macdonald, wanted to provide her DECO1400 students with a web based application that could evaluate their HTML5 code for their course. Our application allows users to validate HTML through direct input, as well as uploading their own files they've written. We've even included a way for users to view the file structure of their website, and see files they've incorrectly linked, allowing users to check their entire project in one go!

Other HTML evaluators are often difficult for entry level users to understand. The focus here of the application is communicating solutions to the problems they find. We provide users with informative fixes to the problems they encounter. It's as much a validator as it is a learning tool. No other sort of web application exists to serve as in this manner - it's cutting edge.

\section*{Dot Points to Hit}

\begin{itemize}
\item Web specifications are forgiving and tolerant
\item Old validators no longer relevant
\item Forgiving nature - doesn't help teaching best practice
\item Miss key areas like accessibility
\item Client wanted to provide DECO1400 students with an web based evaluation service
\item Evaluate HTML files and websites - validity, best practice
\item Includes a file structure display - users see whole webpage
\item Focus is on communicating solutions
\item One of the first of its kind
\end{itemize}

\end{document}